---
title: 'The Spacekime Analytics of EEG, ECG, and Behavior with Multiple Doses of tDCS'
author: "<h3>SOCR/MIDAS (Yuan-Yu Lin)</h3>"
date: "`r format(Sys.time(), '%B %Y')`"
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(ggfortify)

library(manipulateWidget)
library(transport)
library(shapes)
library(TCIU)
library(DT)
library(ggplot2)

library(R.matlab)
library(plotly)
library(dplyr)
library(tidyr)
library(spatstat)
library(akima)

```

## import the data

### The dataset is from the <https://figshare.com/articles/figure/Dataset_of_Concurrent_EEG_ECG_and_Behavior_with_Multiple_Doses_of_transcranial_Electrical_Stimulation-_Stimulation_Trials_PSD/14810517>

```{r}
# import  Experiment_1 0101

##  setwd('/Users/waynelin/Desktop/umich/SOCR/R_code/EEG_ECG_Behavior/Exp1_Raw Data/0101')


path_Exp1 <- "/Users/waynelin/Desktop/umich/SOCR/R_code/EEG_ECG_Behavior/Exp1_Raw Data"
path_0101<- file.path(path_Exp1, "0101")


EEG_0101_raw_data <- readMat(file.path(path_0101, "EEG_DS_Struct_0101.mat"))
behavioral_CTT_0101_raw_data <- read.csv(file.path(path_0101, "0101", "ptracker-0101.csv"))

head(EEG_0101_raw_data)
str(EEG_0101_raw_data)

head(behavioral_CTT_0101_raw_data)
str(behavioral_CTT_0101_raw_data)

```

### understand the data structure -

#### 

#### DSamp

triggers \<- These are all the labeled EEG/Stimulation start/stop
triggers

EEGdata \<- Contains the downsampled EEG/ECG/EOG voltage data dims: 35
channelss X \~4E6 samples

fs \<- The downsampled sampling frequency of the data : 1000 Hz.
#####1000 samples per second.

fsOld \<- The original sampling frequency of the data

time \<- Time vector for the data. Should be 1 X \~4E6

label \<- Contains the channel label information. BIP1= ECG, BIP2=EOG,
RESP1= N/A

nchan \<- The number of channels in the data

rate \<- Redundant to fs, sampling rate of data

npt \<- Number of data points \~4E6

Subj \<- Subject and session that data belong to. I.e. 0302 - Subject 03
session 03

ptrackerPerf \<- The CTT data deviation/ the behavioral data

ptrackerTime \<- Time vector for the CTT data

ptrackerfs \<- The sampling frequency for the CTT data 100 Hz. (source:
<https://github.com/ngebodh/GX_tES_EEG_Physio_Behavior>)

```{r}
## Prepare the data for analyze

EEG_data_0101 <- EEG_0101_raw_data[["DSamp"]][[2]]
EEG_time_0101 <- EEG_0101_raw_data[["DSamp"]][[5]]
channel_label <- EEG_0101_raw_data[["DSamp"]][[6]]


# Create a data frame for plotting(test)

test_channel_range <- 1:3
test_sample_range <- 1:600000 #. 10 minutes



eeg_subset <- EEG_data_0101[test_channel_range, test_sample_range]
time_subset <- EEG_time_0101[test_sample_range]
test_channel_label <- channel_label[test_channel_range]
channel_labels <- sapply(test_channel_label, function(x) x[[1]])

plot_test_df <- data.frame(Time = rep(time_subset, times = length(test_channel_range)),
                 Channel = factor(rep(paste0("Ch", test_channel_range), each = length(test_sample_range))),
                 Voltage = as.vector(t(eeg_subset)))
plot_test_df$Channel <- factor(plot_test_df$Channel,
                                      levels = c("Ch1", "Ch2", "Ch3"),
                                      labels = channel_labels)





```

```{r}
## create dataframe and export as CSV file

create_sub_df_fun<- function(EEG_dataset, EEG_time_dataset , channel_range_variable, time_range_variable){
  eeg_subset <- EEG_dataset[channel_range_variable, time_range_variable]
  time_subset <- EEG_time_dataset[time_range_variable]
  test_channel_label <- channel_label[channel_range_variable]
  channel_labels <- sapply(test_channel_label, function(x) x[[1]])
  
  internal_fun_df <- data.frame(Time = rep(time_subset, times = length(channel_range_variable)),
                   Channel = factor(rep(paste0("Ch", channel_range_variable), each = length(time_range_variable)), 
                   levels = paste0("Ch", channel_range_variable), labels = channel_labels),
  Voltage = as.vector(t(eeg_subset)))

  return (internal_fun_df)
}

#combine the function of create_sub_df_function and output_csv_ fun 
create_sub_df_and_export_csv <- function(EEG_dataset, EEG_time_dataset , channel_range_variable, time_range_variable, CSV_name){
  internal_create_df <- create_sub_df_fun(EEG_dataset, EEG_time_dataset , channel_range_variable, time_range_variable)
  output_csv_fun(internal_create_df, CSV_name)
}


# export all dataframe and save in one csv file 
output_csv_fun <- function(input_df, csv_name){
  write.csv(input_df, file = csv_name, row.names = FALSE)
}

create_sub_df_and_export_csv(EEG_data_0101, EEG_time_0101,1:35, 1:4227788, "EEG_all_channel_all_time.csv")

# export each channel data frame and save  csv file
export_specific_channel <- function(channel_number){
  test_channel_label <- channel_label[channel_number]
  channel_labels <- sapply(test_channel_label, function(x) x[[1]])
  export_name_for_csv <- paste0("EEG_",channel_labels,"_all_time.csv")
  export_x <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, channel_number, 1:4227788)
  output_csv_fun(export_x,export_name_for_csv)
}

for (ch in 1:35) {
  export_specific_channel(ch)
}



```

### Calculate mean values for each channel

```{r}
plot_test_df_binned <- plot_test_df %>%
  mutate(Time_bin = round(Time, 2)) %>%  # rounds time to 0.01s
  group_by(Time_bin, Channel) %>%
  summarize(mean_voltage = mean(Voltage, na.rm = TRUE), .groups = "drop")


```

### Create interactive plot

```{r}
EEG_0101_interactive_plot_test <- plot_ly() %>%
  add_trace(data = plot_test_df, x = plot_test_df$Time, y = plot_test_df$Voltage, color = plot_test_df$Channel, type = 'scatter', mode = 'lines') %>% 
  layout(title = "Interactive plot between first 3 channels over ten minutes", xaxis = list(title = "Time (sec)"), yaxis = list(title = "Voltage"))
EEG_0101_interactive_plot_test


```

# transfer the plot_test_df to CSV format

```{r}
# output Long Format to csv file
filter_data_frame <- function(input_dataFrame, filter_variable) {
  # Filter the data frame where Channel matches filter_variable
  filtered_df <- input_dataFrame[input_dataFrame$Channel == filter_variable, ]
  return(filtered_df)
}
combine_fun <- function (origin_df, target_df){
  temp_df = data.frame()
  
}

test_Fp1_df <- filter_data_frame(plot_test_df,"Fp1")
test_Fpz_df <- filter_data_frame(plot_test_df, "Fpz")
test_Fp2_df <- filter_data_frame(plot_test_df, "Fp2")

channel_name_label_fun <- function(channel_name){
  out_put = paste0("Voltage_", channel_name)
  return (out_put)
  }

combine_test_df_fun <- function(to_df, target1_df, target2_df){ 
  to_df_name <- unique(to_df$Channel)
  target1_df_name <- unique(target1_df$Channel)
  target2_df_name <- unique(target2_df$Channel)
  to_df <- to_df[, c("Time", "Voltage")]
  df1 <- target1_df[, c("Time", "Voltage")]
  df2 <- target2_df[, c("Time", "Voltage")]
  names(to_df)[2] <- channel_name_label_fun(to_df_name)
  names(df1)[2] <-channel_name_label_fun(target1_df_name)
  names(df2)[2] <-channel_name_label_fun(target2_df_name)
  combined_df <- merge(to_df, df1,by = "Time")
  combined_df <- merge(combined_df, df2,by = "Time" )
  return (combined_df)
}

combined_three_df <- combine_test_df_fun(test_Fp1_df,test_Fp2_df,test_Fpz_df)
head(combined_three_df)



output_csv_fun(plot_test_df, "test_multiple_channel.csv")
output_csv_fun(test_Fp1_df, "test_Fp1_output.csv")
output_csv_fun(test_Fp1_df, "test_Fpz_output.csv")
output_csv_fun(test_Fp1_df, "test_Fp2_output.csv")
output_csv_fun(combined_three_df, "Fp1_Fpz_Fp2_output.csv")


```

### Generate the kime-phases

```{r}
Fp1_10min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 1:600000)
Fp1_20min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 600001:1200000)
Fp1_30min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 120001:1800000)
Fp1_40min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 1800001:2400000)
Fp1_50min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 2400001:3600000)
Fp1_60min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 3600001:4200000)
Fp1_70min_df <- create_sub_df_fun(EEG_data_0101,EEG_time_0101, 1:1, 4200001:length(length(EEG_data_0101[1:1,])))


output_csv_fun(Fp1_10min_df, "Fp1_10min.csv")
output_csv_fun(Fp1_20min_df, "Fp1_20min.csv")
output_csv_fun(Fp1_30min_df, "Fp1_30min.csv")
output_csv_fun(Fp1_40min_df, "Fp1_40min.csv")
output_csv_fun(Fp1_50min_df, "Fp1_50min.csv")
output_csv_fun(Fp1_60min_df, "Fp1_60min.csv")
output_csv_fun(Fp1_70min_df, "Fp1_70min.csv")


```




```{r}
## testing !!!

### create the 3D kimesurfaces for 0.1 minutes of fp1 channel 
#  Fp1_10min_df is 600000 obs. of  3 variables(Time, channel name, voltage)
#  Time - 1000Hz
#  channel name - Fp1
#  voltage - each 0.001 sec's voltage of EEG


## 0521
file_name = "exp1_0101_Fp1"
Fp1_path<- file.path(file_name, "Fp1_10min.csv")
Fp1_10min_df <- read.csv(Fp1_path)


# head(Fp1_10min_df) ## 600000 obs. of  3 variables:

slice_fp1 = split(Fp1_10min_df, ceiling(seq_along(1:nrow(Fp1_10min_df)) / 100)) # 0.1 sec 

fp1_time = slice_fp1[[1]]$Time     ## 60000 obs. of  3 variables
length_time = length(fp1_time)   # should small than 100

# # Generate 8 kime-phases meet 
##  # randomly generate 8 phi kime-phases for each of the 100 time
num_row <- 8
num_col <- 100  

phi_8_vec <- matrix(NA, ncol=num_col, nrow = num_row)
#if(rand_opt=="laplace"){
for (t in 1:num_col) { 
  # for a given t, generate 8 new phases
  set.seed(t);
  phi_8_vec[ ,t] <-
    extraDistr::rlaplace(num_row,mu=0,sigma=0.5)
  # rank-order the phases for consistency
  # within the same foliation leaf
  phi_8_vec[ ,t] <- sort(phi_8_vec[ ,t])
  # force phases in [-pi: pi)
  for (i in 1:num_row) {
    if (phi_8_vec[i,t] < -pi) 
      phi_8_vec[i,t] <- -pi
    if (phi_8_vec[i,t] >= pi) 
      phi_8_vec[i,t] <- pi
  }
}

voltage= slice_fp1[[1]]$Voltage


# reconstructed the data frame
phi_containter <- NULL
for (i in 1:num_row) {
  phi_containter <- c(phi_containter, phi_8_vec[i])
}

phi_containter <- as.vector(phi_8_vec)  
time_vec <- rep(1:num_col, each = num_row)  
source_vec <- rep(1:num_row, times = num_col) 

reconstruct_df <- data.frame(time = time_vec, source = source_vec, phi = phi_containter, voltage = voltage)
# head(reconstruct_df)



#set plotly matrix  211 * 211 kime-domain Cartesian

matrix_size <- num_col* 2 +11  # 111
half_matrix_size <- (matrix_size-1)/2   # 105
matrix_Fp1_10 <- matrix(NA, nrow=matrix_size, ncol = matrix_size) # size = 211 * 211

#  using phase-based x-y coordinates to fill the matrix_Fp1_10
for (t in 1:num_col) {
  for (p in 1:num_row) {
    x = half_matrix_size+1+t*cos(phi_8_vec[p,t])
    y = half_matrix_size+1+t*sin(phi_8_vec[p,t])
    matrix_Fp1_10[x,y]  <- voltage[(p-1)*num_col +t]
  }
}


# Reduce the noise, sigma = 5
matrix_Fp1_10_smooth <- (1/10000)*as.matrix(blur(as.im(matrix_Fp1_10), sigma=5))
# max(matrix_Fp1_10_smooth)
# 2.275602e-15
# min(matrix_Fp1_10_smooth)
#  -2.153322


x <- vector()
y <- vector()
i <- 1
for (t in 1:num_col) {
  for (p in 1:num_row) {
    x[i] = half_matrix_size+1  +t*cos(phi_8_vec[p,t])
    y[i] = half_matrix_size+1+t*sin(phi_8_vec[p,t])
    i <- i+1
  }
}

# label of each data
hoverText <- cbind(x=1:matrix_size, y=1:matrix_size, height=as.vector(t(matrix_Fp1_10_smooth))) # tail(mytext)
custom_txt <- matrix(NA, nrow=matrix_size, ncol=matrix_size)

for (x in 1:matrix_size) {
  for (y in 1:matrix_size) {
    t = sqrt((x-half_matrix_size-1)^2 + (y-half_matrix_size-1)^2)
    p = atan2(y-half_matrix_size-1, x-half_matrix_size-1)
    custom_txt[x,y] <- paste('Height: ', round(hoverText[(x-1)*matrix_size+y, 3], 3),
                             '\nTime (t) ', round(t, 4),
                             '\nPhase (Ï†)', round(p, 4))}}




# Set up surface grid
xx2 <- half_matrix_size+1 + seq(0,half_matrix_size,1/2) %o% cos(seq(-pi, pi, 2*pi/(matrix_size-1)))
yy2 <- half_matrix_size+1 + seq(0,half_matrix_size,1/2) %o% sin(seq(-pi, pi, 2*pi/(matrix_size-1)))
zz2 <- matrix_Fp1_10_smooth

# Axes and title
word_font <- list(family = "Courier New, monospace", size = 10, color = "black")
x_axis <- list(title = "kime-magnitude (t) [Cartesianð‘¥ axis] ", titlefont = word_font)

y_axis <- list(title = "kime-phase (Ï†) [Cartesian y axis]", titlefont = word_font)
z_axis_range <- c(min(matrix_Fp1_10_smooth) , max(matrix_Fp1_10_smooth))
z_axis <- list(title = "intensity [Cartesian z axis]", titlefont = word_font, range = z_axis_range) # z- axis range
title_name <- list(text = "3D kimesurfaces for 0.1 second of Fp1 channel", font = word_font)
legend_set <- list(title = "intensity", x = 1.05, y = 1, font = list(size = 10), bgcolor = "rgba(255,255,255,0.5)")


## plot_ly the graph
fp1_0.1sec_kime_surface <- plot_ly(
  x = ~xx2, y = ~yy2, 
  z = ~zz2,
  type = "surface",
  showscale = TRUE,
  colorbar = legend_set,
  text = custom_txt,
  hoverinfo = "text"
) %>%
  layout(
    title = title_name,
    scene = list(
      xaxis = x_axis,
      yaxis = y_axis,
      zaxis = z_axis
    )
  )

fp1_0.1sec_kime_surface


```






```{r}
##  The function is to create the 3D kimesurfaces 
##  parameter 
###   long_data_frame - 100 obs. of  3 variables(Time, channel, voltage)
###   title_label - the title of kimesurface
### return 
##    list [1] - reconstruct_df with itme ,phi, voltage
###   list [2] -  plot_1 - image of kimesurface

kime_surface_fun<- function(long_data_frame, title_label ){
  
  time_data <- long_data_frame$Time
  min_time <- min(time_data)
  max_time <- max(time_data)
  length_data <- length(long_data_frame$Time)
  max_time <-max(long_data_frame$Time)
  
  if(length_data > 100){
    stop("please load the data frame with less than 100 in time")
  }
  num_row <- 8
  num_col <-length_data
  # # Generate 8 kime-phases meet 
  ##  # randomly generate 8 phi kime-phases for each of the 100 time

  
  phi_8_vec <- matrix(NA, ncol=num_col, nrow = num_row)
  #if(rand_opt=="laplace"){
  for (t in 1:num_col) { 
    # for a given t, generate 8 new phases
    set.seed(t);
    phi_8_vec[ ,t] <-
      extraDistr::rlaplace(num_row,mu=0,sigma=0.5)
    # rank-order the phases for consistency
    # within the same foliation leaf
    phi_8_vec[ ,t] <- sort(phi_8_vec[ ,t])
    # force phases in [-pi: pi)
    for (i in 1:num_row) {
      if (phi_8_vec[i,t] < -pi) 
        phi_8_vec[i,t] <- -pi
      if (phi_8_vec[i,t] >= pi) 
        phi_8_vec[i,t] <- pi
    }
  }
  
  voltage= long_data_frame$Voltage
  
  # reconstructed the data frame
  phi_containter <- NULL
  for (i in 1:num_row) {
    phi_containter <- c(phi_containter, phi_8_vec[i])
  }
  
  phi_containter <- as.vector(phi_8_vec)  
  time_vec <- rep(1:num_col, each = num_row)  
  source_vec <- rep(1:num_row, times = num_col) 
  
  reconstruct_df <- data.frame(time = time_vec, source = source_vec, phi = phi_containter, voltage = voltage)
  
  #set plotly matrix  211 * 211 kime-domain Cartesian
  matrix_size <- num_col* 2 +11  
  half_matrix_size <- (matrix_size-1)/2   
  matrix_plotly <- matrix(NA, nrow=matrix_size, ncol = matrix_size) 
  
  #  using phase-based x-y coordinates to fill the matrix
  for (t in 1:num_col) {
    for (p in 1:num_row) {
      x = half_matrix_size+1+t*cos(phi_8_vec[p,t])
      y = half_matrix_size+1+t*sin(phi_8_vec[p,t])
      matrix_plotly[x,y]  <- voltage[(p-1)*num_col +t]
    }
  }
  
  # Reduce the noise, sigma = 5
  matrix_plotly_smooth <- (1/10000)*as.matrix(blur(as.im(matrix_plotly), sigma=5))
  
  
  # label of each data
  hoverText <- cbind(x=1:matrix_size, y=1:matrix_size, height=as.vector(t(matrix_plotly_smooth))) # tail(mytext)
  custom_txt <- matrix(NA, nrow=matrix_size, ncol=matrix_size)
  
  for (x in 1:matrix_size) {
    for (y in 1:matrix_size) {
      t = sqrt((x-half_matrix_size-1)^2 + (y-half_matrix_size-1)^2)
      p = atan2(y-half_matrix_size-1, x-half_matrix_size-1)
      custom_txt[x,y] <- paste('Height: ', round(hoverText[(x-1)*matrix_size+y, 3], 2),
                               '\nTime (t) ', round(t, 2),
                               '\nPhase (Ï†)', round(p, 2))}}
  
  
  # Set up surface grid
  xx2 <- half_matrix_size+ 1 + seq(0,half_matrix_size,1/2) %o% cos(seq(-pi, pi, 2*pi/(matrix_size-1)))
  yy2 <- half_matrix_size+1 + seq(0,half_matrix_size,1/2) %o% sin(seq(-pi, pi, 2*pi/(matrix_size-1)))
  zz2 <- matrix_plotly_smooth
  
  # Axes and title
  word_font <- list(family = "Courier New, monospace", size = 10, color = "black")
  x_axis <- list(title = "kime-magnitude (t) [Cartesianð‘¥ axis] ", titlefont = word_font)
  
  y_axis <- list(title = "kime-phase (Ï†) [Cartesian y axis]", titlefont = word_font)
  z_axis_range <- c(min(matrix_plotly_smooth) , max(matrix_plotly_smooth))
  z_axis <- list(title = "intensity [Cartesian z axis]", titlefont = word_font, range = z_axis_range) # z- axis range
  title_name <- list(text = title_label, font = word_font)
  legend_set <- list(title = "intensity", x = 1.05, y = 1, font = list(size = 10), bgcolor = "rgba(255,255,255,0.5)")
  
  
  ## plot_ly the graph
  plot_1 <- plot_ly(
    x = ~xx2, y = ~yy2, 
    z = ~zz2,
    type = "surface",
    showscale = TRUE,
    colorbar = legend_set,
    text = custom_txt,
    hoverinfo = "text"
  ) %>%
    layout(
      title = title_name,
      scene = list(
        xaxis = x_axis,
        yaxis = y_axis,
        zaxis = z_axis
      )
    )
  return(list(reconstruct_df, plot_1))
  
}


```



```{r}
# downsample e dataset   100 rows in order to meet the loading structure of kimesurfaces function

# read the data from csv format and return the data
read_csv_from_each_channel <- function(path, name){
  path_way <- file.path(path, name)
  data_ <- read.csv((path_way))
  return (data_)
}

library(dplyr)
# The function is to manipulate the data structure toward the kime_surface_fun funtion's need

data_manipulation_fun <- function(df){
  num_total <- nrow(df)
  num_bin <- 100
  df$bin <- cut(seq_len(num_total), breaks = num_bin, labels = FALSE)
  new_df <- df %>%
  group_by( bin) %>%
  summarise(
  Time = round((mean(Time)/1000),3), 
  Voltage = round(mean(Voltage),2),
  .groups = "drop"
  )
  return(new_df)
}

# This function is to read the file from csv, shrink rows number to less than 100 
# and print the kimsurface 
data_manipulation_and_kimesurface <-function(filePath, fileName, Kimesurface_title){
  read_df <- read.csv(filePath)
  rebuild_df <- data_manipulation_fun (read_df)
  ouput_kimesurface <- kime_surface_fun(rebuild_df, Kimesurface_title)[2]
  return (ouput_kimesurface)
}



```

```{r}

# each 10 mins of Fp1 channel and its kimesurface.

file_name = "exp1_0101_Fp1"
Fp1_10_path<- file.path(file_name, "Fp1_10min.csv")
Fp1_20_path<- file.path(file_name, "Fp1_20min.csv")
Fp1_30_path<- file.path(file_name, "Fp1_30min.csv")
Fp1_40_path<- file.path(file_name, "Fp1_40min.csv")
Fp1_50_path<- file.path(file_name, "Fp1_50min.csv")
Fp1_60_path<- file.path(file_name, "Fp1_60min.csv")
Fp1_70_path<- file.path(file_name, "Fp1_60min.csv")
Fp1_all_time_path <- file.path(file_name, "EEG_Fp1_all_time.csv")

data_manipulation_and_kimesurface(Fp1_10_path, "Fp1_10min.csv" , "3D kimesurfaces for 0 to 10 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_20_path, "Fp1_20min.csv" , "3D kimesurfaces for 10 to 20 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_30_path, "Fp1_30min.csv" , "3D kimesurfaces for 20 to 30 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_40_path, "Fp1_40min.csv" , "3D kimesurfaces for 30 to 40 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_50_path, "Fp1_50min.csv" , "3D kimesurfaces for 40 to 50 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_60_path, "Fp1_60min.csv" , "3D kimesurfaces for 50 to 60 minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_70_path, "Fp1_70min.csv" , "3D kimesurfaces for 60 above minutes of fp1 channel")
data_manipulation_and_kimesurface(Fp1_all_time_path, "EEG_Fp1_all_time" , "3D kimesurfaces for all time of fp1 channel")


```


```{r}
## Fp2 channel kimesurface

Fp2_alltime_df <- read_csv_from_each_channel(path_each_channel, "EEG_Fp2_all_time.csv")
fp2_100row <- data_manipulation_fun(Fp2_alltime_df)
fp2_kimesurface <- kime_surface_fun(fp2_100row, "3D kimesurfaces of Fp2 (all time)")[2]
fp2_kimesurface
```


```{r}
## Fpz channel kimesurface


Fpz_alltime_df <- read_csv_from_each_channel(path_each_channel, "EEG_Fpz_all_time.csv")
fpz_100row <- data_manipulation_fun(Fpz_alltime_df)
fpz_kimesurface <- kime_surface_fun(fpz_100row, "3D kimesurfaces of Fpz (all time)")[2]
fpz_kimesurface
```

```{r}
Fz_alltime_df <- read_csv_from_each_channel(path_each_channel, "EEG_Fz_all_time.csv")
fz_100row <- data_manipulation_fun(Fz_alltime_df)
fz_kimesurface <- kime_surface_fun(fz_100row, "3D kimesurfaces of Fz (all time)")[2]
fz_kimesurface
```



```{r}





```


```{r}

```

